04_estimation

### 2019-08-13 02_parks_data.Rmd
Add twitter data to analysis
Also estimate models given the coefficients found by Kinnell, et al.

Now we can join the cemeteries data to the parks data and write out the results
```{r write}
rbind(
  dissolved %>% 
    transmute(id = parknum, name = park_name, acres, courts, playgrounds, trails, 
              type = "park"),
  dissolved_cemeteries %>% 
    transmute(id = source_id, name, acres, courts = FALSE, playgrounds = FALSE, 
              trails = FALSE, type = "cemetery")
  ) %>%
  filter(as.numeric(acres) > 0.5) %>%
  st_simplify(preserveTopology = TRUE) %>%
  write_rds("data/open_spaces.rds") %>%
  geojsonio::geojson_write(file = "data/open_spaces.geojson")
```

>>>>

Now we can join the cemeteries data to the parks data and write out the results.
```{r write}
open_spaces <- rbind(
  dissolved %>% 
    transmute(id = parknum, name = park_name, acres, courts, playgrounds, trails, 
              type = "park"),
  dissolved_cemeteries %>% 
    transmute(id = source_id, name, acres, courts = FALSE, playgrounds = FALSE, 
              trails = FALSE, type = "cemetery")
  ) %>%
  filter(as.numeric(acres) > 0.5) %>%
  st_simplify(preserveTopology = TRUE) %>%
  write_rds("data/open_spaces.rds")

geojsonio::geojson_write(open_spaces, file = "data/open_spaces.geojson")
```

### 2019-08-13 03_logsums.Rmd
Add twitter data to analysis
Also estimate models given the coefficients found by Kinnell, et al.

```{r setup}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(sf)
library(spdep)
library(leaflet)
```

@@

@@

We use this function with asserted beta values of -1.98 and 0.3 to calculate the
accessibility logsum.
```{r logsum_vars}
logsum_vars <- tracts %>%
  transmute(
    geoid, 
    # Log-sum based utilities, without and with Twitter data
    access_ls = calculate_park_logsums(
      log(distances) * -1.98, log(open_spaces$acres) * 0.3
    ),
    # Normalize the logsum onto the Z-scale
    access_ls_n = (access_ls - mean(access_ls) ) / sd(access_ls)
  ) %>%
  st_set_geometry(NULL)
```

@@

tracts_access <- tracts %>%
  left_join(logsum_vars, by = "geoid") %>%
  mutate(walk_10 = ifelse(geoid %in% inside_access$geoid, TRUE, FALSE)) %>%
  write_rds("data/tracts_acces.rds")
```

Here's a map of the values 
```{r access_map}
# this interactive map is much easier to create and explore
pal <- colorQuantile("GnBu", tracts_access$access_ls_n, n = 5)
bin <- colorFactor("Dark2", tracts_access$walk_10)
leaflet(tracts_access) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(group = "access", color = ~ pal(access_ls_n),
              label = ~as.character(round(access_ls_n,2))) %>%
  # addPolygons(group = "tweets", color = ~ pal(tweets_ls),
  #             label = ~as.character(round(tweets_ls,2))) %>%
  addPolygons(group = "10-minute walk", color = ~ bin(walk_10)) %>%
  addLayersControl(baseGroups = c("access", "tweets", "10-minute walk"))
```

>>>>

```{r setup}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(sf)
library(spdep)
library(leaflet)
library(lubridate)
```

@@

## Tweet Counts

We obtained geolocated tweets sent from within the boundaries of each park for
the period from July through October, 2014.

```{r tweets}
tweets <- read_csv("data/tweet_counts.csv") %>%
  filter(id %in% open_spaces$id) %>%
  gather(date, count, PK_7_1:PK_10_31) %>%
  separate(date, c("pk", "month", "day"), sep = "_") %>%
  mutate(date = as_date(str_c("2014", month, day, sep = "-"))) %>%
  dplyr::select(id, date, count) %>%
  mutate(
    month = month(date, TRUE),
    wday = wday(date, TRUE)
  ) 
```

We have a question about how consistent the twitter data is by month or across
days of the week. Somewhat surprisingly, the twitter activity is lowest on saturday, 
and then next lowest on Sunday.

```{r wday}
tweets %>%
  ggplot(aes(x = wday)) +
  geom_bar()
```

August is very low! Let's make sure to use September or October.

```{r month}
tweets %>%
  ggplot(aes(x = month)) +
  geom_bar()
```

Let's look at the within-park consistency or variability of twitter activity.
It appears that there is some variation, but that parks with high use typically 
have high use.

```{r consistency}
tweets %>%
  filter(month == "Sep") %>%
  ggplot(aes(x = date, y = count + 1, group = id)) +
  geom_line(alpha = 0.5) + scale_y_log10()
```

Let's calculate the weekday average for each park in September and then go with
that.

```{r tweets_summary}
(tweets_summary <- tweets %>%
  filter(month == "Sep") %>%
  #filter(!wday %in% c("Sat", "Sun")) %>%
  group_by(id) %>%
  summarise(
    tweet_average = mean(count),
    tweet_count = sum(count)
  ) %>%
  arrange(-tweet_count))
ggplot(tweets_summary, aes(x = tweet_count)) +
  geom_histogram()

open_spaces <- open_spaces %>%
  left_join(tweets_summary, by = "id") %>%
  mutate_at(
    vars(starts_with("tweet")), 
    funs(replace_na(., 0))
  ) 
```

@@

We use this function with asserted beta values of -1.98 and 0.3 to calculate the
accessibility logsum.
```{r logsum_vars}
open_spaces$acres <- as.numeric(open_spaces$acres)
logsum_vars <- tracts %>%
  transmute(
    geoid, 
    # Log-sum based utilities, without and with Twitter data
    access_ls = calculate_park_logsums(
      log(distances) * -1.768, log(open_spaces$acres) * 0.373
    ),
    tweets_ls = calculate_park_logsums(
      log(distances) * -1.768, 
      log(open_spaces$acres) * 0.373 + 
        0.1 * yeo.johnson(open_spaces$tweet_count, lambda = 0)
    ),
    multi_ls = calculate_park_logsums(
      log(distances) * -1.768, 
      log(open_spaces$acres) * 0.373 + 
        open_spaces$trails * 0.99 + 
        open_spaces$playgrounds * 0.26 + 
        open_spaces$courts * 0.43
    ),
  ) %>%
  mutate_at(
    vars(ends_with("_ls")),
    # Normalize the logsum onto the Z-scale
    funs( (. - mean(.) ) / sd(.))
  ) %>%
  st_set_geometry(NULL) %>%
  as_tibble()
```

@@

tracts_access <- tracts %>%
  left_join(logsum_vars, by = "geoid") %>%
  mutate(walk_10 = ifelse(geoid %in% inside_access$geoid, TRUE, FALSE)) %>%
  write_rds("data/tracts_access.rds")
```

Here's a map of the values. Note that there is also a shiny app in this project that
allows the user to set different values for the logsum parameters.
```{r access_map}
# this interactive map is much easier to create and explore
pal <- colorQuantile("GnBu", c(tracts_access$access_ls, tracts_access$multi_ls), n = 5)
bin <- colorFactor("Dark2", tracts_access$walk_10)
leaflet(tracts_access) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(group = "access", color = ~ pal(access_ls),
              label = ~as.character(round(access_ls, 2))) %>%
  addPolygons(group = "tweets", color = ~ pal(tweets_ls),
              label = ~as.character(round(tweets_ls, 2))) %>%
  addPolygons(group = "Kinner", color = ~ pal(multi_ls),
              label = ~as.character(round(multi_ls, 2))) %>%
  addPolygons(group = "10-minute walk", color = ~ bin(walk_10)) %>%
  addLayersControl(baseGroups = c("access", "tweets", "Kinner", "10-minute walk"))
```

### 2019-08-13 04_estimation.Rmd
Add twitter data to analysis
Also estimate models given the coefficients found by Kinnell, et al.

```{r loaddata}
tracts_access <- read_rds("data/tracts_acces.rds")
W <- read_rds("data/W.rds")
trMC <- trMC <- trW(as(W, "CsparseMatrix"), type="MC")
tracts_sp <- as(tracts_access, "Spatial")
```

@@

```{r spatial selection}
physact_base_sem <- errorsarlm(update(base_formula, physact ~ .),
                               data = tracts_sp, listw = W, zero.policy = TRUE)
physact_base_sdm <- lagsarlm(update(base_formula, physact ~ .),
                             data = tracts_sp, listw = W, zero.policy = TRUE,
                             type = "mixed")
test_sdmsem <- lmtest::lrtest(physact_base_sem, physact_base_sdm)
```

```{r access_sdm}
# estimate models
pa_access_sem <- update(physact_base_sem, .~ . + access_ls)
pa_quarter_sem <- update(physact_base_sem, .~ . + walk_10)

pa_models <- list("Base" = physact_base_sem,
                  "Access: logsum" = pa_access_sem,
                  "Access: 10-min walk" = pa_quarter_sem)
```

```{r screen_pa_models}
view_kable(
htmlreg(pa_models, digits = 4, table = FALSE, single.row = TRUE, 
                   caption.above = TRUE, caption = "Spatial Error Model ",
          stars = c(0.001, 0.01, 0.05, 0.1) )
)
```

```{r}
view_kable <- function(x){
  tab <- paste(capture.output(x))
  tf <- tempfile(fileext = ".html")
  writeLines(tab, tf)
  viewer <- getOption("viewer")
  viewer(tf)
}
```

@@

```{r screen_obesity_models}
screenreg(obesity_models, digits = 4, table = FALSE)
```

```{r screen_obese_models, eval = FALSE}
  screenreg(obesity_models, digits = 4, table = FALSE, ci.force = TRUE,
          single.row = TRUE, caption = "Spatial Error Model Estimates of Effect on Obesity Rates",
          caption.above = TRUE, custom.coef.names = c(
            "(Intercept)", "log(Density)", "log(Income)",
            "Fulltime", "College-educated",  "Single Adults",
            "Youth (0-17)", "Young adults (18-34)",
            "Seniors (65+)", "Black population share",
            "Asian population share",
            "Hispanic population share", "Other Minorities",
            "Physical activity",
            "Spatial correlation", "Access: Logsum", "Access: 10-min walk"
          ))
```

```{r obesityplot}
names_for_terms <- c(
  "(Intercept)", "log(density)", "log(Income)",
  "Fulltime", "College-educated",  "Single Adults",
  "Youth (0-17)", "Young adults (18-34)",
  "Seniors (65+)", "Black population share",
  "Asian population share",
  "Hispanic population share", "Other Minorities",
  "$\\gamma$: spatial correlation","Physical activity",
  "Access: Logsum", "Access: 10-min walk"
)
termnames <- tibble(
  name = names_for_terms,
  term = c("Intercept", "log(density)", "log(income)", "fulltime", "college", "single",
           "youth", "young_adults", "seniors", "black", "asian", "hispanic", "other",
           "lag", "physact", "access_ls", "walk_10TRUE"))
source("R/impacts_extractor.R")
obesity_impacts <- lapply(obesity_models, function(x) impacts_extractor(x, trMC)) %>%
  bind_rows(.id = "model")  %>%
  left_join(termnames, by = "term") %>%
  mutate(name = factor(name, levels = rev(names_for_terms)))

ggplot(obesity_impacts %>% filter(effect == "Total"), 
       aes(x = name, ymin = `2.5%`, ymax = `97.5%`,  y = `50%`, color = model)) +
  geom_abline(slope = 0, intercept = 0, color = "gray") +
  geom_errorbar(position = "dodge2") +
  scale_color_brewer("Model", palette = "Set1") +
  #geom_point(position = "dodge2") +
  ylab("Simulated Total Impact on Obesity Rate") +
  coord_flip() +
  #facet_wrap(~effect) +
  theme_bw() +
  theme(legend.position = "bottom", 
        axis.text.y = element_text(size = 10),
        axis.title.y = element_blank())
```

>>>>

```{r loaddata}
tracts_access <- read_rds("data/tracts_access.rds")
W <- read_rds("data/W.rds")
trMC <- trMC <- trW(as(W, "CsparseMatrix"), type="MC")
tracts_sp <- as(tracts_access, "Spatial")
```

The base formula includes all of the tract-level covariates.

@@

```{r}
names_for_terms <- c(
  "(Intercept)", "log(Density)", "log(Income)",
  "Fulltime", "College-educated",  "Single Adults",
  "Youth (0-17)", "Young adults (18-34)",
  "Seniors (65+)", "Black population share",
  "Asian population share",
  "Hispanic population share", "Other Minorities",
  "$\\gamma$: spatial correlation","Physical activity",
  "Logsum", "Tweets", "Attributes", "10-min walk"
)

termnames <- tibble(
  name = names_for_terms,
  term = c("Intercept", "log(density)", "log(income)", "fulltime", "college",
           "single", "youth", "young_adults", "seniors", "black", "asian", 
           "hispanic", "other",
           "lag", "physact", "access_ls", "tweets_ls", "multi_ls", "walk_10TRUE"))
```

We estimate an SEM and SDM version of the base formula, to see if a LRT can 
exclude the SDM. It doesn't, so we use the SDM going forward. This makes the 
impacts analysis a little more difficult, but it's not a huge deal.

```{r spatial selection}
physact_base_sem <- errorsarlm(update(base_formula, physact ~ .),
                               data = tracts_sp, listw = W, zero.policy = TRUE)
physact_base_sdm <- lagsarlm(update(base_formula, physact ~ .),
                             data = tracts_sp, listw = W, zero.policy = TRUE,
                             type = "mixed")
(test_sdmsem <- lmtest::lrtest(physact_base_sem, physact_base_sdm))
```

Now we can add all four access measures to the formula one after the other.

```{r access_sdm}
# estimate models
pa_access_sdm  <- update(physact_base_sdm, .~ . + access_ls)
pa_tweets_sdm  <- update(physact_base_sdm, .~ . + tweets_ls)
pa_multi_sdm   <- update(physact_base_sdm, .~ . + multi_ls)
pa_walk10_sdm  <- update(physact_base_sdm, .~ . + walk_10)

pa_models <- list("Base"        = physact_base_sdm,
                  "Logsum"      = pa_access_sdm,
                  "Tweets"      = pa_tweets_sdm,
                  "Attributes"  = pa_multi_sdm,
                  "10-min walk" = pa_walk10_sdm)
```

```{r screen_pa_models}
view_kable <- function(x){
  tab <- paste(capture.output(x))
  tf <- tempfile(fileext = ".html")
  writeLines(tab, tf)
  viewer <- getOption("viewer")
  viewer(tf)
}
view_kable(
htmlreg(pa_models, digits = 4, table = FALSE, single.row = TRUE, 
                   caption.above = TRUE, caption = "Spatial Error Model ",
          stars = c(0.001, 0.01, 0.05, 0.1) )
)
```

Let's look at the impacts. The total effect of each park access measure is
significant at the 95% level. Indeed, it is the only

```{r impacts}
source(here("R/impacts_extractor.R"))

pa_impacts <- lapply(pa_models, function(x) impacts_extractor(x, trMC)) %>%
  bind_rows(.id = "model")  %>%
  left_join(termnames, by = "term") %>%
  mutate(name = factor(name, levels = rev(names_for_terms)))

ggplot(pa_impacts, 
       aes(x = name, ymin = `2.5%`, ymax = `97.5%`,  y = `50%`, color = model)) +
  geom_abline(slope = 0, intercept = 0, color = "gray") +
  geom_errorbar(position = "dodge2") +
  facet_wrap(~effect, scales = "free_x") +
  scale_color_brewer("Model", palette = "Set1") +
  #geom_point(position = "dodge2") +
  ylab("Simulated Total Impact on Physical Activity Rate") +
  coord_flip() +
  #facet_wrap(~effect) +
  theme_bw() +
  theme(legend.position = "bottom", 
        axis.text.y = element_text(size = 10),
        axis.title.y = element_blank())
```

@@

```{r screen_obesity_models}
view_kable(
  htmlreg(obesity_models, digits = 4, table = FALSE, single.row = TRUE, 
                   caption.above = TRUE, caption = "Spatial Error Model ",
          stars = c(0.001, 0.01, 0.05, 0.1) )
)
```

```{r obesityplot}
obesity_impacts <- lapply(obesity_models, function(x) impacts_extractor(x, trMC)) %>%
  bind_rows(.id = "model")  %>%
  left_join(termnames, by = "term") %>%
  mutate(name = factor(name, levels = rev(names_for_terms)))

ggplot(obesity_impacts, 
       aes(x = name, ymin = `2.5%`, ymax = `97.5%`,  y = `50%`, color = model)) +
  geom_abline(slope = 0, intercept = 0, color = "gray") +
  geom_errorbar(position = "dodge2") +
  facet_wrap(~effect, scales = "free_x") +
  scale_color_brewer("Model", palette = "Set1") +
  #geom_point(position = "dodge2") +
  ylab("Simulated Total Impact on Physical Activity Rate") +
  coord_flip() +
  #facet_wrap(~effect) +
  theme_bw() +
  theme(legend.position = "bottom", 
        axis.text.y = element_text(size = 10),
        axis.title.y = element_blank())
```

```{r models}
write_rds(pa_models, "data/pa_models.rds")
write_rds(obesity_models, "data/obesity_models.rds")
```
